\documentclass{article}
\usepackage{amssymb}
\pagestyle{empty}

\setlength{\topmargin}{-.5in}
\setlength{\oddsidemargin}{-.25in}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}

\everymath{\displaystyle}

\begin{document}


{\bf Math 220}\hfill{Name:}

{\bf Homework 1: Validity and Soundness}
\vspace{.3in}


\begin{enumerate}
\item Assume that the truth-value assignments for each statement are correct.
\begin{itemize}
\item[(1)] All Linfield math students are sleep-deprived. (True)
\item[(2)] All sleep-deprived people are goofy. (True)
\item[(3)] All sleep-deprived people are Linfield math students. (False)
\item[(4)] All Linfield math students are goofy. (True)

\end{itemize}
 Now given these assigned truth-values, determine the validity and soundness of each of the following arguments:
 
 \begin{enumerate}
 \item All Linfield math students are sleep-deprived.\\
 \underline{All sleep-deprived people are goofy.}\\
 $\therefore$ All Linfield math students are goofy. 
 \vspace{1in}
 
 \item All Linfield math students are goofy.\\
  \underline{All sleep-deprived people are goofy.}\\
  $\therefore$ All Linfield math students are sleep-deprived.
   \vspace{1in}
  
  \item All sleep-deprived people are Linfield math students. \\
  \underline{All Linfield math students are goofy.}\\
  $\therefore$ All sleep-deprived people are goofy.
   \vspace{1in}
  
  \item All sleep-deprived people are goofy.\\
   \underline{All Linfield math students are goofy.}\\
   $\therefore$ All Linfield math students are goofy.
 \end{enumerate}
 
 \break
 \item Using this new set of statements and assigned truth-values, 
 \begin{itemize}
 \item[(1)] All talented people are insightful. (True)
 \item[(2)] All talented people are rich. (False)
 \item[(3)] All college students are rich. (False) 
 \item[(4)] All college students are talented. (False)
 \item[(5)] All rich people are insightful. (False)
 \item[(6)] All college students are insightful. (False)
 \item[(7)] All rich people are college students. (False)
 
 \end{itemize}
 
 construct arguments with TWO premises such that:
 
 \begin{enumerate}
 \item The argument is valid, but both premises and the conclusion are false.
 
 \vspace{1.4 in}
 
 \item The argument is valid, but both premises are false, and the conclusion is true.
 
 \vspace{1.4 in}

 \item The argument is valid, one premise is true and one false, and the conclusion is true.
 
 \vspace{1.4 in}
 
  \item The argument is valid, one premise is true and one false, and the conclusion is false.
 
 \vspace{1 in}

 
 \end{enumerate}
 \break
 
 \item Indicate which of the following statements are true. Be prepared to explain why in class. For those that are false, show why they are false by giving an example.
 
 \begin{enumerate}
 \item Every argument with a false conclusion is invalid.
 \vspace{1.1 in}
 
 \item Every argument with a false premise is invalid.
 \vspace{1.1in}
 
 \item Every argument with a false premise and a false conclusion is invalid.
 \vspace{1.1 in}
 
  \item Every argument with a false premise and a true conclusion is invalid.
 \vspace{1.1 in}

 \item Every argument with true premises and a false conclusion is invalid.
 \vspace{1.1 in}

 \item Every argument with a true conclusion is sound.
 \vspace{1.1 in}
 
  \item Every argument with a false conclusion is unsound.
 \vspace{.5 in}
\end{enumerate}
\end{enumerate}
\end{document}